Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-08 main.tex
done with first draft of intro

In summary, this paper contains the following contributions:

>>>>

Combinatorial proofs and deep infernence can be seen as opposite ends
of a spectrum: whereas deep inference allows for a very fine
franularity of inference rules---one inference rule in a standard
formalism, like sequent calculus or semantic tableaux, is usually
simulated by a sequence of different deep inference rules---have
combinatorial proofs comletely abolished the concept of inference
rule. Nonetheless, there is a close relationship between the two,
realized through a decomposition theorem, as we establish it in this
paper.
